---
title: "Statistical Analysis on the Effect of Supplements on Guinea Pigs"
author: "Janina Reyes"
date: "January 23, 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC). 



## Variables used

```{r ToothGrowth, echo = TRUE}
summary(ToothGrowth)
```

## Shiny Application

The link to the application is indicated:

https://jeareyes17.shinyapps.io/dataproductscourseproject/

- The user can view the comparison between the type of supplements taken, whether orange juice or vitamin C or the dosage taken.

- The shiny application displays the following:
  a. Boxplot between for each classification
  b. Summary of the fitted model

## Source

- McNeil, D. R. (1977). Interactive Data Analysis. New York: Wiley. 

- Crampton, E. W. (1947). The growth of the odontoblast of the incisor teeth as a criterion of vitamin C intake of the guinea pig. The Journal of Nutrition, 33(5), 491–504. doi: 10.1093/jn/33.5.491. 




